Test-driven Knowledge Graph Construction

### 2023-05-08 doc/paper4.tex
Fix incorrectly changed sh:targetNode
SHACL targets are terms, not subgraphs

    \item Wrap the queries as SPARQL-based SHACL constraints to automate their execution. SHACL defines a target\footnote{\urlshacltargets} of each constraint. In our context, a target sets the scope of a CQ. The scope of the data graph validated by a given constraint may either encompass the entire knowledge graph or cover its subset. For instance, existentially quantified queries checking the complete data graph can target it by using \texttt{sh:targetNode}. It is also possible to rewrite a part of a SPARQL query translating a CQ as target selection in SHACL. Alternatively, the prerequisite part of the query can be represented as a SPARQL-based target \cite{SHACLAF2017}. An~entity-centric partitioning can be implemented by defining a SPARQL-based target that covers a concise bounded description \cite{Stickler2005}. Some data sources for the knowledge graph may natively partition data to independent subsets, such as API responses or messages from a queue, that can be effectively validated by specific subsets of SHACL constraints. SHACL also defines the criteria of correctness of the SPARQL queries. An \texttt{sh:ask} query is expected to return the boolean \texttt{true}, while any results produced by an sh:select query are treated as violations. Specific expected results can be either hard-coded into the queries or specified via \texttt{sh:hasValue} in case a single value is expected. When including the expected results in SPARQL-based constraints, we may run into the limitations of SHACL due to pre-binding of variables.\footnote{\urlshaclprebinding} For example, the \texttt{VALUES} clause, which could represent results of \texttt{SELECT} queries, is not allowed.

>>>>

    \item Wrap the queries as SPARQL-based SHACL constraints to automate their execution. SHACL defines a target\footnote{\urlshacltargets} of each constraint. In our context, a target sets the scope of a CQ. The scope of the data graph validated by a given constraint may either encompass the entire knowledge graph or cover its subset. For instance, existentially quantified queries checking the complete data graph can target it by using \texttt{sh:targetNode []}. It is also possible to rewrite a part of a SPARQL query translating a CQ as target selection in SHACL. Alternatively, the prerequisite part of the query can be represented as a SPARQL-based target \cite{SHACLAF2017}. An~entity-centric partitioning can be implemented by extracting concise bounded descriptions~\cite{Stickler2005} of the targeted entities. Some data sources for the knowledge graph may natively partition data to independent subsets, such as API responses or messages from a queue, that can be effectively validated by specific subsets of SHACL constraints. SHACL also defines the criteria of correctness of the SPARQL queries. An \texttt{sh:ask} query is expected to return the boolean \texttt{true}, while any results produced by an sh:select query are treated as violations. Specific expected results can be either hard-coded into the queries or specified via \texttt{sh:hasValue} in case a single value is expected. When including the expected results in SPARQL-based constraints, we may run into the limitations of SHACL due to pre-binding of variables.\footnote{\urlshaclprebinding} For example, the \texttt{VALUES} clause, which could represent results of \texttt{SELECT} queries, is not allowed.
